Paradigms in Physics 2.0

### 2017-06-27 paper.tex
work on summary

When we had obtained feedback from the entire faculty, we scheduled
\emph{two} faculty meetings (DURATION?).  In the first meeting, we
presented our proposal in detail.  This was needed for several
reasons.  Those faculty we met with first may not have seen the final
proposal.  Some faculty during their individual meetings chose to
focus on a small subset of the curriculum, often relating to courses
they had themselves taught.  In one meeting we presented the proposal
and fielded questions.  In a second faculty meeting, we again
presented our proposal, and

\emph{How did we do it?}

\emph{Faculty vote}

@@

\section{Summary}
\emph{Rearticulate big ideas. Shadowing}

\emph{Future research: Document learning trajectories, new courses.  pre-/post-,
  understanding sense-making.}

@@

\acknowledgments{This paper is based upon work supported by the
  National Science Foundation under Grant No. 1323800 Supplement.}

>>>>

When we had obtained feedback from the entire faculty, we scheduled
\emph{two} faculty meetings (DURATION?).  In the first meeting, we
presented our proposal in detail.  This was needed for several
reasons.  Those faculty we met with first may not have seen the final
proposal.  Some faculty during their individual meetings chose to
focus on a small subset of the curriculum, often relating to courses
they had themselves taught.  In one meeting we presented the proposal
and fielded questions.  In a second faculty meeting, we again
presented our proposal, and opened the floor for discussion.  After
considerable discussion, we unanimously voted to adopt the proposed
changes.

@@

\section{Summary}
We have developed a significant incremental change to the Paradigms
curriculum.  This change focused on the first two big ideas underlying
the Paradigms: (1) close attention to content ordering, and (2)
developing a consensus and understanding of the curriculum among our
faculty members.  Our commitment to using active engagement in our
upper-division curriculum remains unchanged.  While the specific
content ordering we developed is interesting, the \emph{process} by
which we reached it, and developed a faculty consensus is at the
essence of what makes distinctive the Paradigms in Physics program.
The process of developing faculty understanding of the Paradigms is
ongoing, as we are having professors new to the Paradigms shadow
experienced faculty as they teach in the Paradigms, prior to teaching
the courses themselves..

Future work will involve documenting the learning trajectories that we
have developed in our curriculum.  Furthermore, we are engaging in a
project to study our students' development of sense-making skills in
particular through the two new courses that are intended specifically
to ramp up those skills (instincts?).

We look forward to another two decades of the Paradigms!

@@

\acknowledgments{This work was supported by the National Science
  Foundation under Grant No. 1323800 Supplement.}
